---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# ch.fso.es.rs

The ch.fso.es.rs package provides versioned time series data
and their meta information for scientific research.
In addition, the package contains the
extract-transform-load (ETL) functionality that
sources the data from its original provider.

## Browse Time Series Data

You can use GitHub's ability to render to csv to explore the datasets

## Basic Data Consumption via opentimeseries


```r
remotes::install_github("opentsi/opentimeseries")
library(opentimeseries)

# first param `series` defaults to NULL
# fetches all series from `remote_archive`
ts <- read_open_ts(
  remote_archive = "opentsi/ch.fso.es.rs"
)

ts
```
Given a unique time series identifier and a GitHub repo,
*opentimeseries* will return a time series and long format `data.table`.

## Basic Usage

```{r, eval=FALSE}
ts <- read_open_ts(
  remote_archive = "opentsi/ch.fso.es.rs"
)
```

By specifying a date in addition, you can able to obtain other versions
but the most recent one. The *opentimeseries* package will simply select
the most recent release that was available at the selected date.

```{r, eval=FALSE}
ts202307 <- read_open_ts(
  remote_archive = "opentsi/ch.fso.es.rs",
  date = "2023-07-01"
)
```

Because time series data can get revised, storing vintages is important
to monitor data revisions and benchmark forecasts. Here's a quick visual
comparison:

# please insert your main series you want to showcase visually
# to replace this example! 
```{r}
library(opentimeseries)
library(tsbox)

ts <- read_open_ts(series = "tot.tot",
  remote_archive = "opentsi/ch.fso.es.rs"
)
ts202307 <- read_open_ts(series = "tot.tot",
  remote_archive = "opentsi/ch.fso.es.rs",
  date = "2023-07-01"
)
ts202307$id <- "tot.tot.202307"
ts$id <- sprintf("tot.tot.202605")
ts_plot(rbind(ts202307, ts))
```

